Predicting Sales Level for Newly Published Books \\ using Cost-Sensitive Ensemble Methods

### 2016-12-08 paper.tex
improving the SoA

%\textbf{UNDER CONSTRUCTION}

>>>>

The most used technique to tackle sales forecasting problems is time-series prediction methods
\cite{Chu2003,Brown1959,Winters1960,Box1969,Papalexopoulos1990,KayacanUK10},
however the correctness of the problem data strongly affects the predictions obtained.
Moreover, this kind of methods are based on using historical data to make time series.
However, in the case of new products sales prediction (such as the issue of new books), 
there is no available historical sales data \cite{ChingChin2010}, 
and only pre-sales data are available \cite{FaderHardie2005,Madsen2008}, 
i.e. variables known before the product is on sale.

Not only the lack of historical data makes this a complex problem, but also the fact 
that several variables (seasonality, promotions, or fashions) might influence predictions
\cite{Lapide1999,Thomassey2012,Xia2012,SThomassey2014,ChernWSF15}.

Due to the difficulty this problem represents when forecasting sales of new 
products, some authors have proposed using different data mining methods, such as
data clustering and fuzzy neural networks \cite{Chang2009}  or
extreme learning machine with adaptive metrics of inputs \cite{Xia2012}.
In this sense, several authors have proposed using ensemble of models for sales forecasting, 
as in \cite{ChiJie2012}, where a hybrid forecasting model integrates ensemble 
empirical model decomposition and extreme learning machine to develop an effective 
forecasting model for computer products sales.
Also, Meulstee et al. \cite{Meulstee2008} developed an ensemble learning approach 
for better handling of seasonal changes and fluctuations in consumer demands,
while Chang et al. \cite{Chang2006715} integrated a fuzzy logic controller 
and artificial neural network for sales forecasting in printed circuit board industry.
Another authors have faced the problem of sales forecasting in textile-apparel 
fashion industry (a very similar issue to the new book publishing problem) 
using a clustering method together with decision trees, as in \cite{SThomassey2014},  or
a forecasting method based on extreme machine learning with adaptive metrics of inputs \cite{Xia2012}.

% TODO
